This report has been produced using open source tools such as {\LaTeX} \cite{lamport1994ldp} and \emph{git} \cite{chacon2009pg}.
{\LaTeX} is widely used in academia to prepare print-class documents.
It automatically takes care of numbering, cross-referencing, tables of contents, bibliography, etc.
\emph{Git} is a high performance distributed revision control which is used in many open source projects, such as the linux kernel.
Git makes it easy and safe to collaborate as each contributor works on his or her own personal copy.
Good contributions can be easily shared with others, and it is always possible to revert to a previous version.

Our git repository is publicly available in \emph{github}:

https://github.com/jbarcelo/C4EU-deliverables

Anyone who is familiar with {\LaTeX} and \emph{github} can contribute to this document.
The first step is to make a copy (a \emph{fork} in \emph{github} jargon).
The contributor can work on this copy and make changes to improve the document.
After that, it is necessary to request that these changes are merged into the original copy of the document (a \emph{pull request} in github jargon).

If you see anything that can be improved, feel free to contribute.
This document is alive in the sense that it will keep evolving as long as contributors make changes and improve it.

The system automatically keeps track of all the contributors and their contributions. 
It is possible to see who is contributing more actively and which are the exact changes made by each contributor.
And everything is public on the web.
