Once the C4EU project is finished, the tools put in place specifically for its execution, that is to say, the BuB mailing list and the bubforeurope website, will be kept operational. Their continuity is guaranteed because they are hosted in guifi.net Foundation facilities and the domain names are owned by this organisation. The activity in the mailing list may decrease due to the pilots completion. The new bubforeurope website has been already designed and implemented rather statically, pursuing to reduce to the minimum the maintenance requirements. The only remaining tasks to be done in the coming weeks are to integrate the documentation of the third reporting period and to introduce the changes resulting of the review process. After that the website will be considered to be finished, being available to anyone willing to contribute and to maintain it.

The rest of the tools presented in the previous section have been integrated in the guifi.net ecosystem, thus, their continuity is guaranteed by the fact of being used by a wide community.

The FONN Compact must be proofread, preferentially by native English speakers. Aside from language aspects, its adoption by another communities  would contribute in great manner at making it less dependent of the Spanish legal system and less guifi.net focused. In this sense, one potential approach could be to generate a more abstract document containing the fundamentals of Community Networks to be used by BuB initiatives as a reference and as a starting point for their licenses.

Now that the major efforts to translate guifi.net website have already been done, that is to say, to put the translation facilities in place and to translate the most important documents, it is expected that the translation of the remaining parts will not be abandoned. Moreover, the increase of the participation in international projects such as C4EU is significantly stimulating the generation of English documentation.

The conflicts resolution tools must be translated into English. The adoption by other communities would bring similar benefits as the adoption of the FONN Compact.

Inside guifi, the economic compensation methodology must be extended to all remaining PoPIX and existing OF nodes and hybrid nodes must be documented using the new features.

